\documentclass[10pt]{article}

\usepackage{mathpazo}
\usepackage{setspace}
%\usepackage{natbib}
%\usepackage{tipa}
\usepackage{graphicx}
%\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[dvipsnames]{color}
%\usepackage{cancel}
%\usepackage[normalem]{ulem}
%\usepackage{qtree}
%\usepackage{linguex}
%\renewcommand{\refdash}{}
%\usepackage{tree-dvips}
%\usepackage{cgloss}
%\usepackage{txfonts}
%\usepackage{times}
\usepackage{units}
%\usepackage{avm}
\usepackage{color}
\definecolor{darkblue}{rgb}{0,0,.45}
\definecolor{blue}{rgb}{0,0,.6}
\definecolor{maroon}{rgb}{.4,0,0}
\definecolor{lightgrey}{rgb}{.7,.7,.7}
\usepackage[pdfborder=0 0 0, colorlinks=true, linkcolor=darkblue, urlcolor={blue}]{hyperref}
\usepackage[vmargin=1.2in, hmargin=1.2in, a4paper]{geometry}
%\addtolength{\topmargin}{-0.75in}
%\addtolength{\textheight}{1.00in}

%\bibliographystyle{lsalikealt}

\newcommand{\bss}{\char`\\\hspace{-.45ex}\char`\\} % Stupid backslash, esp. in code
\newcommand{\bs}{\char`\\} % Stupid backslash, esp. in code
\newcommand{\code}[1]{{\texttt{{\color{lightgrey}\raisebox{.45ex}{$\ulcorner$}\hspace{-.5ex}{\color{maroon}#1}\hspace{-.54ex}\raisebox{.45ex}{$\urcorner$}}}}}

\title{Term Paper: \\[1.0em] \Large{\textit{Moses ist je und je nicht wohl beredt gewesen}}}

\begin{document}
\maketitle


\begin{spacing}{1.35}

If you have your own idea for a paper you can talk with me about your idea.
Otherwise, write about the errors of Moses output, doing all of the following:

\begin{itemize}
\item Analyze Moses' output of text from three different genres/domains/registers.
	You can use any language pair.
	Quantitatively \& qualitatively document the following types of errors:\footnote{You can use another translation error classification scheme if you want.}
 \begin{spacing}{0.9}
 \begin{enumerate}
  \item Morphological (inflection / compounding)
  \item Syntactic (word order / fluency)
  \item Lexical (word choice)
  \item Deletions
  \item Any cultural errors/deficiencies\footnote{For example, most English speakers don't know what an \textit{Amerikaner} cookie is, nor have they ever heard of \href{https://en.wikipedia.org/wiki/Dinner_for_One}{\textit{Dinner for One}}.  So if a German text references either of these, the English translation would need a short explanation of what these are.}
  \item Any other types of errors.  Specify the type of error
 \end{enumerate}
 \end{spacing}

 Show examples to illustrate these.\footnote{List both the incorrect translation and what you think would be a good translation.}
 Also use charts and/or tables that summarize your quantitative analysis.
 Are there differences between genres/domains/registers in the frequencies of different types of errors?
 For example, does a genre have more cultural or fewer syntactic errors compared to another genre?
 If there are differences, why?

\item Identify which types of errors would also be made by a human translator, which types of errors are limited to any machine translation system (including Google/Bing Translate), and which errors would only be made by the Moses phrase-based system.
	%You do not necessarily need to run the texts through Google/Bing translate, just say 
	Why?

\item Conduct a small experiment to see if you are faster at translating the text by yourself, or editing Moses' output.
	Ensure that half of the text is first translated by you, and half is first translated by Moses (and then edited by you).
	Discuss the results.

\end{itemize}

I'm mostly concerned about the content of your paper, but for consistency the paper should be approximately 10--15 pages, normal margins, 1.5x spacing, 11pt serif font (eg.~Palatino, Garamond, Minion, Constantia, Times New Roman).
If you have any questions or requests for modifications, feel free to ask me.


\end{spacing}
%\bibliography{localbib}
\end{document}
